New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs

### 2020-02-23 Paper/Abstract_name.tex
updates before submitting to Public Choices

\title{New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}}
\author{
Mathilde Maurel\thanks{CNRS, France and Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France} 
\and Thomas Pernet\thanks{Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France,
\href{mailto:t.pernetcoudrier@gmail.com}{email: t.pernetcoudrier@gmail.com} 
%email: \href{t.pernetcoudrier@gmail.com}
}
}

@@

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
\pagebreak \newpage

\doublespacing

\section{Introduction} \label{sec:introduction}

The case of China offers an illustration of the dilemma many nations face between the objectives concerning development and poverty reduction on the one hand and those of fighting against pollution on the other. Environmental protection is sometimes at odds with poverty reduction, as the steps required to reduce poverty may entail a cost in terms of pollution to build infrastructure and stimulate economies. Despite this cost, in 2005, China launched a set of vigorous measures aimed at combatting growth-induced pollution and environmental degradation. The question to be addressed here is whether this voluntary approach is sufficient and whether it can bring about the desired outcomes.

The Chinese model of development is characterized by its dualism \citep{Vahabi1995-fm}, as a model of federalism that implies a specific trade-off between political cost and economic benefit seen in the still ongoing planning of the economy and the concomitant liberalization of market forces \citep{Berglof1998-oc,Qian1998-yf}. As a consequence, China's political decision to reduce growth-induced pollution emissions is rooted in its FYP (Five Years Plan) strategy and the enforcement of political objectives by the central government, which aims at keeping pollution under control. Is its approach efficient? This paper provides an answer to this question. It stresses the relative efficiency of state regulation by highlighting the strength of Chinese firms' policy-induced responses.

Moreover, this paper also shows that, while private firms have been sensitive to the new environmental targets and have made significant reductions in their emissions of pollutants, State-Owned Enterprises (SOEs) have not taken similar steps. SOEs' inaction in this regard has been widely viewed as an outcome of the 'soft budget constraint' (SBC) \citep{Kornai2003-nv}. It is a term initially coined by Janos Kornai (\citeyear{Kornai1993-kg, Kornai1995-cu, Kornai1998-ek, Kornai2001-bw}), who referred to the phenomenon of bailing-out loss-making firms that consequently undermines ex-ante incentives.

The concept of the SBC sees a straightforward application to the objective of sustainable growth: under the condition that they have rational expectations to be refinanced, as in the case of SOEs, enterprises will not be motivated to reach their objective of reducing pollution. Furthermore, the presence of the SBC among certain groups of enterprises (SOEs) implies that there is a harder budget constraint for other enterprises. In reference to the case of former Yugoslavia, \cite{Kraft1992-iy} demonstrate that, while the manufacturing sector was a net beneficiary of redistribution, its SBC was compensated for by a harder budget constraint in the private business sector.

This reasoning holds in many other circumstances, as are described in this paper, which establishes that private firms have to adjust and decrease pollution more vigorously than they should need to, in order to compensate for the weak restructuring and weak adoption of green innovations by SOEs. A final but significant element to be discussed is innovation, and research and development (R\&D). Interestingly, \cite{Huang1998-pi} argue that SOEs and large corporations tend to maintain the stability of their R&D organizations.

The lack of effective ex-post screening mechanisms in large corporations and SOEs makes them tend to choose safer innovative projects. In contrast, green projects are usually risky and are more likely to be undertaken by small or private firms. It translates to private firms benefiting from higher returns from environmental incentives than SOEs.

The objective of this paper is as follows. First, it intends to evaluate the efficiency of the new environmental policy launched during the 11th FYP, by paying particular attention to cities targeted by the central government, called TCZ cities. Are the industries located in those cities, particularly the most polluting ones, more successful in fighting against pollution and meeting the new targets in terms of pollution reduction? Second, the paper examines whether SOEs behave differently as compared with private firms. We expect that SOEs will invest a lower amount of resources in meeting the requirements imposed by the environmental policy. We start the analysis by presenting the main characteristics of the Chinese environmental policy before 2006 and up to 2010, which corresponds to the period of our dataset.

Then, in the following section, we discuss the empirical specification and the dataset. Section \ref{sec:empirical} sets-up the empirical analysis, main results, robustness checks. Section \ref{sec:channels} develops the transmission mechanisms by paying special attention to the impact of environmental policies on Total Factor Productivity (TFP) and we distinguish TFP for private firms as opposed to SOEs. Finally, this paper concludes in Section \ref{sec:conclusion}.

\section{Policy Background} \label{sec:Policy}

The Chinese policymakers decided to take the environmental issue seriously after the sulfur dioxide (SO2) peak hurt the country in 1995. In no less than three years, the officials in Beijing proposed and ratified a law regulating SO2 emissions. In 1998, the \textit{'Acid Rain Control Zones and Sulfur Dioxide Pollution Control Zones'} policy, abbreviated as \textit{'Two Control Zone'} (TCZ), was implemented by the central government, to control the emissions of this pollutant.

While the regulation of SO2 emissions was initially designed to be implemented at the national level, the State Council subsequently chose 175 cities with very poor environmental records to engage with more effort. Three selection criteria were decided according to the environmental performance preceding the regulations. A city was placed under scrutiny if the average annual ambient SO2 concentration was higher than the national Class II standard (0.06mg/m3), if the daily average ambient SO2 concentration exceeded the national Class III standard (0.25mg/m3)\footnote{China uses its air quality standard, which is less stringent than the WHO's standard. China's National Environmental Monitoring Center (CNEMC) has real-time, hourly air quality data for major cities in China. The real-time data is available at \href{http://www.cnemc.cn/}. Major air pollutants, including SO2, NO2, and PM10, are monitored. To evaluate air quality, the Chinese government applies three classes. Class 1 means the yearly SO2 level is less than 0.02 mg/m3, or a daily average of less than 0.05mg/m3. Class 2 is less restrictive. The yearly average should not exceed 0.06 and a daily average of about 0.15. Class 3 is consistent with bad air quality. The yearly average can exceed 0.10 mg/m3, and the daily average is 0.25. By contrast, the WHO recommends a daily average of less than 0.02mg/m3. For the record, exposure to high SO2 levels dangerously affects health. According to the WHO 'SO2 can affect the respiratory system and the functions of the lungs and causes irritation of the eyes. Inflammation of the respiratory tract causes coughing, mucus secretion, aggravation of asthma, and chronic bronchitis and makes people more prone to infections of the respiratory tract.'}, or if the city experienced significant SO2 emissions \footnote{A city was designated as an acid rain control zone if:
\begin{enumerate}
\item its average PH value of precipitation was equal or smaller than 4.5;
\item its sulfate deposition was above the critical load;
\item its SO2 emissions were large.
\end{enumerate}
}.

These 175 cities are primarily concentrated in two areas: northern China, due to the heavy reliance on coal to power the heating system, and southern China, where the urban-industrial centres emit substantial air pollution and are the source of severe acid rains. These TCZ cities cover 1.09 million square kilometres, in 27 provinces, and they account for 11.4\% of the whole of China's territory.

At the national level, the objectives were the following: the emissions of SO2 were expected to decrease successively in 2000 and 2010, and a special role was devoted to TCZ cities, which were granted the responsibility of achieving the national Class II standard of 0.06mg/m3. The quota of SO2 emissions set by the central government in 2000 should not exceed 24.6 million tonnes – compared with 23.7 million tonnes in 1997 – and emissions in 2010 were expected to decrease even more than emissions in 2000. In 2001, the policymakers strengthened the consistency of the environmental policy called the control policy in the 10th Five-Year-Plan (FYP) (2001-2005). Objectives were set at the national level while their implementation and enforcement were left at the TCZ cities' level.

TCZ cities were allowed to use four methods to achieve pollution reduction targets. They could shut down polluting plants, install new equipment, use cleaner-burning coal and implement stringent monitoring devices. All power stations with a capacity lower than 50,000 kilowatts, or collieries fueled by coal with a sulfur content of 3\%, had to be shut down \footnote{338 small power units, 784 product lines in small cement and glass plants, 404 lines in iron and steel plants, and 1422 additional pollution sources had closed and by May 2001, 4492 high-sulfur coal mines had ceased production in the TCZ area \citep{He2002-ga}}. Furthermore, the central government had the power to cancel construction projects that did not fit the objective of lower SO2 emissions. Industrial plants were forced to meet the environmental standards by installing higher-capacity (more expensive) pollution control equipment \footnote{The second policy is the installation of flue gas desulfurization (FGD) equipment on new and existing coal-fired power plants. At the end of 2005, FGD equipment had been installed on 46.2 GW of coal-fired electricity generation capacity—12 percent of the total \citep{Cao2009-sv}}. Finally, the government carefully monitored the purchase of fuel oil by firms located in TCZ cities. The transportation department was given the charge of supplying fuel oil with a sulfur concentration of less than 2\% or coal with a sulfur concentration of less than 1\%.

The first evaluations of the policy were run in 2000, as reported in  Table \ref{tab:table1}. The emissions of SO2 rose again after a short drop in 1998-1999. By the end of 2000, 102 TCZ cities reached the national Class II standard, while the total industrial SO2 emissions increased by 12\% compared with the previous year \footnote{84.3\% of the most polluting firms achieved the national target in terms of SO2 emissions  (China Environment Yearbook, 2001)}. The entry of China into the WTO in 2001 launched a process of massive industrialisation, economic growth and reduction of poverty \footnote{The WTO membership allows China to achieve some millennium goals}, which was at odds with the achievement of the objective of stricter control over pollution. The consequences of the lack of coordination and the focus on economic growth from the local government led to a historical peak of SO2 emissions in 2005.

The poor results of the environmental policy were attributed to the design of the policy itself. Its main flaw was that the objectives set at the national level were not restrictive enough at the local level. As a result economic growth was strongly emphasised by the central government, which did not provide local municipalities with the incentives to enforce not only economic growth, but also control over pollution. Most of the time, those objectives turned out to be contradictory and could not be achieved contemporaneously \citep{Barbier2019-ce, Brajer2011-wc, Grossman1995-fb, Lee2015-pw}.

\begin{table}[!htbp] \centering
  \caption{SO2 reduction during the subsequent FYPs}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table1}
    \begin{tabular}{lrrrr}
      \toprule
      {} & \multicolumn{2}{l}{Failure} & \multicolumn{1}{l}{Success} \\
      \hline
      &      (1998-2000) & (2001-2005) &  (2006-2010) \\
      \midrule
      \textbf{TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -14\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -7\% & 38\%  & -15\%     &   \\

      \textbf{No TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -4\%  &   \\
      \text{\footnotesize{SO2 \% reduction}} & 21\%  & 64\%  & -11\%     &   \\

      \textbf{All sample} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -10\% & -10\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -2\%     & 45\%  & -13\% &   \\

      \bottomrule
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Sources: Author's own computation \\
      The list of TCZ is provided by the State Council, 1998. "Official Reply to the State Council Concerning Acid Rain Control Areas and Sulfur Dioxide Pollution Control Areas". The information about the SO2 level are collected using various edition of the China Environment Statistics Yearbook. We compute the reduction of SO2 emission using the same methodology as Chen and al.(2018). 
    \end{tablenotes}
\end{table}

In 2006, the central government reconsidered its strategy, changing from a top-down to a bottom-up approach. The two main differences introduced in the 11th FYP (2006-2010) compared with the previous FYP (2001-2005) are the formulation of transparent environmental targets for each TCZ city and the introduction of an environmental target-based evaluation system for the promotion and career achievement of local officials. This target-based evaluation system aims at promoting the efforts toward the objectives considered to be priorities by the central government. It provides a tool for measuring the success of the local administration, making them accountable. The threat imposed by Beijing forces the mayors and party secretaries to adhere to the national policy.

Local officials in TCZ cities paid more attention to the environmental prejudice of economic growth. This new emphasis on environmental concerns from both the central and local governments was followed by immediate and measurable consequences: over 2006 to 2010 the average growth rate of SO2 emissions fell by -14\% (see Table \ref{tab:table1}), and most TCZ cities (95\%) were able to reach the national Class II standard SO2 concentration, with no cities reporting values above the national Class III standard (Report of Ministry of Environmental Protection of the Peoples Republic of China, \citeyear{Ministry_of_Environmental_Protection_of_the_Peoples_Republic_of_China2011-oi}).

\section{Empirical Specification} \label{sec:empirical}

Our identification strategy is based upon two key elements embodied in the 11th FYP. Indeed, by establishing a clear distinction between TCZ versus non-TCZ cities, the 11th FYP allows us to define a group of treated and control cities. While the treated group (TCZ) is expected to fulfill a set of environmental objectives and is under close governmental scrutiny, the other group (non-TCZ) is not. Moreover, the sharp change in the environmental strategy impulsed by the central government in 2006 split the time span into two sub-periods \footnote{As mentioned in section \ref{sec:Policy} Policy Background; the TCZ policy ended in 2010.}: 2001-2005 corresponding to the 10th FYP and 2006-2010 corresponding to the 11th FYP and the enforcement of the environmental policy. This double characteristic enables us to run a difference-in-difference (DD) analysis.

One concern about this strategy is the influence of the most polluting industries on the probability of a city being designated as a TCZ city. If such a relationship holds, it means that the TCZ policy influences the pattern of SO2 emissions. Still, the presence of firms in the most polluting industries determines the other way around the level of pollution and the probability of being qualified as a TCZ city. To address the resulting endogeneity bias, we add an interaction term, which is the TCZ policy times the 11th FYP period times a dummy capturing the most polluting industries in China.

China's political pecking order of firms is enforced through the systematic misallocation of financial resources \citep{Dollar2007-dr} with credit allocation being biased in favor of SOEs \citep{Brandt2003-hu, Ferri2009-lh, Hale2011-ma, Huang2003-oa}, whatever their compliance with the governmental objectives of the FYP. SOEs in China enjoy easier access to credit. They also benefit from more substantial bargaining power when it comes to negotiating the pollution tax system \citep{Wang2003-ar, Wang2005-yy}. As a result, SOEs are less sensitive to the environmental regulation hardening because of their stronger bargaining power and easier access to bank funding.

To assess this lower sensitivity, besides the spatial, industrial, and time dimensions, we add a last but not least ownerships variable – SOEs versus private firms. We argue that SOEs are less likely to react to the environmental regulation because of the soft budget constraint, which dampens the incentive of fighting against pollution and shifts the burden of the environmental adaptation to private companies \footnote{This DDD strategy is used to tackle the endogeneity problem. Regarding Chinese empirical studies, one can refer to \cite{Chen2018-bs,Shi2018-zk, Hering2014-af} or \cite{Cai2016-br}}. The spatial variable captures the SO2 emissions for TCZ versus non-TCZ cities. The industrial variable controls for the bias of having more TCZ cities, be where the most polluting industries are located. The time divide measures the effect of the introduction of more stringent and accountable environmental objectives after 2006 and the launch of the 11th FYP.

The following is the final specification, its difference-in-difference-in-difference (DDD) design accounts for the four levels of variability:

\begin{equation} \label{eq:main}
\begin{aligned} 
\text {Log SO2 emission }_{i k t}=& \alpha (T C Z_{i} \times \text { Polluting sectors }_{k} \times \text { Period }) \\ &+\beta (T C Z_{i} \times \text { Polluting sectors }_{k} \times \text { Period } \times \text { Share SOE }_{k}) \\ & +\theta {X}_{i k t}+\nu_{ik}+\lambda_{it} +\phi_{kt} +\epsilon_{ikt} 
\end{aligned}
\end{equation}

Where $\text {Log SO2 emission }_{i k t}$ is the level of SO2 in city $i$, industry $k$ and at time $t$. The equation includes four right-hand-side variables of interest, a set of control variables and fixed effects. $T C Z_{i}$ reflects the TCZ policy implemented in 1998 and amended in 2005. $\text {  Polluting sectors }_{k}$ is a dummy variable taking the value one for heavily polluting industries $k$, and zero for less polluting ones. $\text { Period }$ is a dummy variable, which is set equal to one when $t$ is strictly above 2005. $\text { Share SOE }_{k}$ refers to a proxy for the relative share of SOEs in industry $k$.

We add three control variables usually found in the literature (Andersen, (\citeyear{Andersen2016-pa, Andersen2017-wf})), which are the $\text{total output}_{ikt}$, $\text{total fixed asset}_{ikt}$, and $\text{employment}_{ikt}$ aggregated at the city $i$, industry $k$ and time $t$. The equation includes a city-year fixed effect $\phi_{it}$, which controls for all city characteristics that differ across cities over time, such as productivity, policies and wages. $\lambda_{kt}$ is an industry-time pair fixed effect which captures the time-varying and time-invariant industry characteristics, e.g., industry-specific technology and government's industrial policies. With the inclusion of fixed effects $\nu_{ik}$, we address the time invariant differences between the cities’ industries, which are key in our approach: while industrial policies are decided at the central level for the whole country, local municipalities orchestrate their implementation differently from one city to another. In our equation, $\epsilon_{ikt}$ represents the error term. This strategy allows us to isolate the effect of stricter environmental policies affecting TCZ cities before and after the 11th FYP. More importantly for the purpose at hand, it allows us to compare the sensitivity of the firm’s ownership to the enforcement of the environmental regulation, on the emissions of SO2.

We expect the coefficient $\alpha$ to be negative and $\beta$ to be positive. TCZ cities emit less SO2 after 2005 in more polluting industries with a larger presence of private firms because policymakers put more pressure on them, while SOEs enjoy a softer budget constraint, hence cope more easily with the regulation. In all regressions, the standard errors are clustered by industry.

\section{Data} \label{sec:data}

Our key interest is the SO2 emissions, which are available at the city–industry–year level. Using various data sources, we construct a dataset including environmental, industrial and economic information at the city–industry–year level over the period 2002 to 2007.

\subsection{SO2 emissions} \label{sec:so2}

The Ministry of Environmental Protection (MEP) has mandated the State Environmental Protection Agency (SEPA) to collect data on the primary sources of pollutants and waste in China since 1980. The SEPA has monitored firms in 39 major industrial sectors that are considered to be heavy polluters. These firms are required to report basic information, such as company name, address, and output. They also answer a very detailed questionnaire about their emissions of major pollutants (e.g. wastewater, COD, SO2, industrial smoke, and dust).

As reported by \cite{Wu2017-bl} and by \cite{Jiang2014-pf}, the resulting dataset embodies 85\% of the emissions of the major pollutants in China. The MEP has implemented strict procedures, such as unexpected visits from experts, to ensure that firms do not misreport their emissions. Having access to the statistics of SO2, a primary air pollutant, our left-hand side variable is $\text {Log SO2 emission }_{i k t}$, which is the logarithm of S02 emissions in city $i$, industry $k$, and year $t$, for 296 four-digits industries, across 228 cities from 2002 to 2007. We define $\text {  Polluting sectors }_{k}$ equal to one when an industry emits more than 68,070 tonnes of SO2 (top 25\% most polluting sectors).

The emissions of SO2 reached a peak in 2005 at 32.41 million tonnes (China Statistical Yearbook on Environment, 2005). Out of the 522 cities monitored by the Chinese Ministry of Environment, about 400 reported an annual average level of SO2 that met the Grade II national standard (0.06mg/m3) and 33 cities met the worst grade (0.10mg/m3). Two years after the 11th FYP was launched, the situation had slightly changed, according to the Ministry of Environment in its annual report on the state of the environment in China \footnote{The report is available \href{http://english.mee.gov.cn/Resources/Reports/soe/soe2007/201}{here}}. 79\% of the audited cities met Grade II, which is two percentage points better than in 2005. In regards to the Grade III criteria, less than 1.2\% of the cities were above the threshold, which corresponds to an improvement of four percentage points from 2005. The most polluted cities are located in Shanxi, Guizhou, Inner Mongolia, and Yunnan provinces.

\subsection{Ownership} \label{sec:ownership}

The National Bureau of Statistics of China (NBS) distinguishes manufacturing data with sales above RMB 5 million for non-SOEs and SOEs. The survey contains detailed information about the name, address, four-digit Chinese industrial classification (CIC), ownership, financial variables, output, sales, fixed assets, etc.

For $\text{share SOE}_k$, we rely on three proxies. The first is SOEs industrial average share of output ($\text{output share SOE}_k$). Alternatively, we compute the SOEs industrial average share of employment ($\text{labour share SOE}_k$), and capital ($\text{capital share SOE}_k$). For instance, the output of the tobacco industry is almost entirely produced by SOEs (96\%), while the transport equipment industry is more balanced with only 40\% of the output produced by SOEs.

\subsection{Two Control Zone} \label{sec:tcz}

In 1998, the State Council launched a vast policy to curb SO2 emissions and to reduce the acid rain. There were 175 cities called TCZ cities located in 27 provinces designated to provide the subsequent effort for controlling SO2 emissions. Out of the 228 cities in our dataset, 140 are qualified as TCZ cities. Table \ref{tab:appendix1} in the appendix provides the list of TCZ cities present in our dataset. $T C Z_{i}$ is a dummy set equal to one if city $i$ belongs to this list.

\begin{table}[!htbp] \centering
    \caption{ Summary statistics by city-industry and city characteristics}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table2}
    \begin{tabular}{lrrrr}
      \multicolumn{1}{l}{\textbf{\small Panel A: City/city-industry}} \\
      \toprule
      & \multicolumn{2}{c}{No TCZ} & \multicolumn{2}{c}{TCZ} \\
      & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{std} & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{std}\\
      %{}                         & mean   & std    & mean   & std    \\
      \midrule
      $SO2_{ikt}$                  & 182,873 & 372,028 & 174,308 & 357,225 \\
      $\text{count share SOE}_k$   & 0.093  & 0.094  & 0.082  & 0.086  \\
      $\text{output share SOE}_k$  & 0.147  & 0.153  & 0.136  & 0.151  \\
      $\text{capital share SOE}_k$ & 0.220  & 0.197  & 0.209  & 0.198  \\
      $\text{labour share SOE}_k$  & 0.188  & 0.162  & 0.176  & 0.162  \\
      $\text{output}_{kit}$        & 0.028  & 0.101  & 0.058  & 0.266  \\
      $\text{capital}_{kit}$       & 0.008  & 0.030  & 0.014  & 0.054  \\
      $\text{labour}_{kit}$        & 0.009  & 0.024  & 0.016  & 0.056  \\
      \bottomrule
      \\ %%% Create second table
      \multicolumn{1}{l}{\textbf{\small Panel B: SO2 emission by city-location}} \\
      \toprule
      {} & \multicolumn{2}{l}{\footnotesize difference (10.000 tons units)} & \multicolumn{2}{l}{variance (\footnotesize \%)} \\
      %& \multicolumn{1}{l}{No TCZ} & \multicolumn{1}{l}{TCZ} & %\multicolumn{1}{l}{No TCZ} & \multicolumn{1}{l}{TCZ}\\
                  & No TCZ   & TCZ      & No TCZ & TCZ  \\
      Location    &          &          &        &      \\
      \midrule
      Full sample &    -192 & -436 &     0.22 & 0.26 \\
      Central     &    -238 & -232 &     0.25 & 0.19 \\
      Coastal     &    -138 & -659 &     0.12 & 0.29 \\
      Northeast   &    -206 &  -89 &     0.30 & 0.08 \\
      Northwest   &    -115 & -277 &     0.21 & 0.31 \\
      Southwest   &    -272 & -503 &     0.31 & 0.29 \\
      Non Coastal &    -215 & -302 &     0.28 & 0.23 \\
      Coastal     &    -140 & -578 &     0.13 & 0.28 \\
      \bottomrule
      \hline
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Sources: Author's own computation \\
      Panel A provides summary statistics for the main variables used in the subsequent empirical analysis. \\
  Panel B provides summary statistics for the SO2 emission (in 10.000 tons) for Chinese cities (228), split into TCZ (140) and non-TCZ (88) cities
      \\
    \end{tablenotes}
\end{table}

Table \ref{tab:table2} Panel A provides information about the characteristics of TCZ and non-TCZ cities. Not only do TCZ cities emit less SO2 over the entire period, but they are also wealthier and more populated. The reason behind the lower level of SO2 emissions is twofold. First, TCZ cities are, by definition, making more effort to execute stringent environmental regulations. Second, the relationship between wealth and the demand for cleaner environmental goods is known to be positive. In the Chinese case, the evidence is provided in \cite{Hering2014-af}. TCZ and richer cities should therefore emit less SO2. In section \ref{sec:robustness}, robustness checks section, we include yearly GDP per capita and population at the city level. The data are borrowed from the China City Statistical Yearbooks 2002–2007.

Panel B (Table \ref{tab:table2}) displays a regional break down of SO2 emissions for TCZ versus non-TCZ cities and for both periods (before and after the 11th FYP). We note that the emissions of SO2 have decreased in both TCZ and non-TCZ cities after the implementation of the 11th FYP. TCZ cities have contributed more to the overall decrease with a reduction by four points higher than non-TCZ cities (or 436 fewer tonnes of SO2 for TCZ versus 191 for non-TCZ).

Furthermore, Panel B also gives a more in-depth overview of the SO2 reduction in the major areas of China. Following \cite{Wu2017-bl}, we split the cities between Coastal, Southwest, Central, Northeast, and Northwest areas \footnote{This province breakdown follows the paper of \cite{Wu2017-bl}. The Central provinces are Anhui, Henan, Hubei, Hunan, Jiangxi, and Shanxi. The Coastal provinces are Beijing, Fujian, Guangdong, Hainan Hebei, Jiangsu, Shandong, Shanghai, Tianjin, and Zhejiang. The Northeastern provinces are Heilongjiang, Jilin, Liaoning. Northwest are Gansu, Inner Mongolia, Ningxia, Qinghai, Shaanxi, and Xinjiang. The Southwestern parts are Chongqing, Guangxi, Guizhou, Sichuan, Yunnan, and Xizang.}. In our sample, the Coastal area of China is composed of ten provinces and has a total of 68 TCZ cities. This area is the wealthiest part of China: it represents the lion's share of national production and attracts the most significant foreign investment flows.

The Southwestern area has five provinces and 24 TCZ cities, while the Central area has six provinces and 38 TCZ cities. The Northern part of China is split into its Western area with six provinces and 13 TCZ cities and Eastern area with three provinces and 11 TCZ cities.

By the end of the 11th FYP, TCZ cities located in the Coastal and Northwest parts of China have been more successful than non-TCZ cities in reducing their SO2 emissions. By contrast, TCZ cities located in the Central part of China have not performed better than non-TCZ cities (the decrease of SO2 emissions has been -231 for the former and -238 for the latter).

\subsection{Control variables} \label{sec:control}

The literature has listed the key determinants of environmental degradation at the firm level (see, for instance, Cole and Elliott, \citeyear{Cole2003-ad} and Cole et al, \citeyear{Cole2008-pj}). Capital intensity affects both the emissions and intensity of pollution \citep{Hering2014-af, Andersen2017-wf}. Firms' size matters: large industries emit more pollutants. The sectoral belonging matters as well, and we use NBS industrial classification to sort firms according to the sector they belong to. We rely on the 2002 four-digit CIC and compute total employment, total output, and total net fixed assets, aggregated at the city-industry-year level. The information is generated from the Annual Survey of Industrial Firms (ASIF) conducted by China's NBS for the period from 2003 - 2007. As reflected in Table \ref{tab:table2} (Panel A), TCZ cities produce and employ more resources.

\section{Empirical Analysis} \label{sec:analysis}

\subsection{Main results}

Table \ref{tab:table3} reports the results of equation \ref{eq:main}. The coefficient of interest measures the effect of the environmental policy on the emissions of SO2 in the polluting sectors, with a particular emphasis on sectors dominated by SOEs. The triple interaction terms $(T C Z_{i} \times \text {  Polluting sectors }_{k} \times \text { Period })$ estimates are all negative and significant, meaning that SO2 emissions felt more significantly in TCZ cities than in non-TCZ cities after the launch of the 11th FYP, in line with our expectations.

Our key assumption is that the effectiveness of the policy is lower in sectors dominated by SOEs, which face a softer budget constraint. We expect, therefore a less negative coefficient (smaller in absolute value) for those sectors. To test this assumption we interact $T C Z_{i} \times \text {  Polluting sectors }_{k} \times \text { Period }$ with the three proxies of the firms' ownerships: in column 1 are SOEs' industrial output share, in columns 2 and 3 are SOEs' share of capital or labour respectively. The four coefficients of interest are all positive and significant, meaning that the policy is attenuated in the polluting sectors where the presence of SOEs is strong. Those firms enjoy preferential treatment and can adopt business strategies less constrained by the new regulation than private firms. They do not need to reduce, cut or relocate the production because they receive financial support from the local government. Softer credit constraint helps them to absorb the costs linked to the policy more efficiently.

\begin{table}[!htb] \centering
  \caption{Soft budget constraint as reflected in the SOEs’ reaction to the TCZ policy in China: Baseline result
}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table3}
    \begin{tabular}{@{\extracolsep{5pt}}lccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{3}{c}{The Dependent variable: $\text{Ln SO2}_{ikt}$} \\
      \cline{2-4}
      \\[-1.8ex] & Output & Capital & Labour \\
      \\[-1.8ex] & (1) & (2) & (3) \\
      \hline \\[-1.8ex]
      $\text{output}_{ikt}$                                                                                  & $-$0.059        & $-$0.059        & $-$0.059        \\
                                                                                                    & (0.114)         & (0.114)         & (0.113)         \\
      $\text{capital}_{ikt}$                                                                                 & 0.929$^{*}$     & 0.933$^{**}$    & 0.937$^{**}$    \\
                                                                                                    & (0.476)         & (0.475)         & (0.474)         \\
      $\text{labour}_{ikt}$                                                                                  & 1.550           & 1.545           & 1.538           \\
                                                                                                    & (1.023)         & (1.023)         & (1.021)         \\
      $TCZ_i \times \text{Polluting}_k \times \text{Period}$                                           & $-$0.298$^{**}$ & $-$0.336$^{**}$ & $-$0.377$^{**}$ \\
                                                                                                    & (0.142)         & (0.154)         & (0.154)         \\
      $TCZ_i \times \text{output share SOE}_{k} \times \text{Period}$                                 & $-$0.824        &                 &                 \\
                                                                                                    & (0.515)         &                 &                 \\
      $TCZ_i \times \text{Polluting}_k \times \text{output share SOE}_{k} \times \text{Period}$        & 1.315$^{**}$    &                 &                 \\
                                                                                                    & (0.609)         &                 &                 \\
      $TCZ_i \times \text{capital share SOE}_{k} \times \text{Period}$                                &                 & $-$0.682$^{*}$  &                 \\
                                                                                                    &                 & (0.399)         &                 \\
      $TCZ_i \times \text{Polluting}_k \times \text{capital share SOE}_{k} \times \text{Period}$       &                 & 1.065$^{**}$    &                 \\
                                                                                                    &                 & (0.513)         &                 \\
      $TCZ_i \times \text{labour share SOE}_{k} \times \text{Period}$                                 &                 &                 & $-$1.020$^{**}$ \\
                                                                                                    &                 &                 & (0.518)         \\
      $TCZ_i \times \text{Polluting}_k \times \text{labour share SOE}_{k} \times \text{Period}$        &                 &                 & 1.532$^{**}$    \\
                                                                                                    &                 &                 & (0.598)         \\
      \hline \\[-1.8ex]
      city-year fixed effects                                                                       & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                                                                   & Yes             & Yes             & Yes             \\
      city-industry fixed effects                                                                   & Yes             & Yes             & Yes             \\
      Observations                                                                                  & 30,676          & 30,676          & 30,676          \\
      R$^{2}$                                                                                       & 0.851           & 0.851           & 0.851           \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

The control system implemented by the 11th FYP significantly decreases the emission of SO2. The coefficient of $T C Z_{i} \times \text {  Polluting sectors }_{k} \times \text { Period }$ takes two values: -.29 (column 1) and -.37 (column 3), which represents a reduction of SO2 ranging from respectively -7,629 (29\% of the average SO2 emissions of a city polluting industry) to -9,652 tonnes (37\%)\footnote{The average 2005 emissions of SO2 for the polluting industries $k$ located in city $i$ is equal to 25.603 tonnes, the reduction of pollution is straightforward: $-.298 * 25.603 = -7,629$ tonnes for column 2, and $-.377*25.603 = -9,652$ for columns 3. These figures are comparable to the official figures which refers to the whole economy, see table \ref{tab:table1}.}.

The output share of SOEs in the polluting sectors varies from 1.3\% to 33\%. Also, given the estimates of equation 1 in Table 3, the environmental policy's effect is smaller where the state size is more prominent. According to a straightforward formula\footnote{The formula is $\beta * (\text{output share SOE}^{\text{90 percentile}^{th}}_k- \text{output share SOE}^{\text{10 percentile}^{th}}_k)$ when $\beta$ is equal to 1.315: $42\% = 1.135* (0.33 - 0.013)$ table \ref{tab:table3} column 1.}, it is smaller by 42\%. This decline in policy efficiency is imputable to the soft budget constraint.

Other control variables have the expected signs: economic growth has severely degraded the environment; GDP, employment and fixed assets are correlated with more emissions of SO2. The inclusion of these variables does not affect the main coefficient of interest.

\subsection{Testing for parallel trends} \label{sec:parallel}

We must check that our strategy satisfies the parallel trends assumption, by showing that TCZ and non-TCZ cities have a similar SO2 emissions trajectories before the treatment (i.e., before the introduction of stringent environmental regulations). One might think for instance, that certain local governments anticipated the implementation of the environmental regulation and decided to enforce it before the treatment year. The test for the parallel trend assumption consists of replacing the treatment variable $\text { Period }$ with yearly dummies. The new specification becomes:

>>>>

\title{New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs}
\author{
Mathilde Maurel\thanks{CNRS, France and Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France} 
\and Thomas Pernet\thanks{Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France,
\href{mailto:t.pernetcoudrier@gmail.com}{email: t.pernetcoudrier@gmail.com} 
%email: \href{t.pernetcoudrier@gmail.com}
}
}

@@

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
\end{titlepage}
